Data description

### 2017-02-14 Data/data_explnation.Rmd
Play a bit with trait-matching functions

>>>>

```{r}
#IB plays with trait matching
head(pooled_data, 20)

#simple match
scatter.smooth(pooled_data$nectar_tube_depth_mm ~ pooled_data$tongue_length)
temp <- pooled_data$tongue_length - pooled_data$nectar_tube_depth_mm 
plot(temp) #A few outlyers, including negative values.

pooled_data[which(temp < 0),c(1,2,12,17)]
#Clearly there is something with Anchusa azurea: Robing? Exerted pollen?
#Andryala integrifolia: idem
#Armeria velutina: Very open tube? idem with convolvulus and equium, rosmarinus...
#one interaction of Astragalus lusitanicus	Oxythyrea funesta, check?
pooled_data[which(temp > 10),c(1,2,12,17)]
#some buterflies
#lots of long tongued bees visiting open flowers (cistus, asphodelus) This is real and suggests a barrier model.

#complex match
temp <- ifelse(pooled_data$IT > pooled_data$nectar_tube_diameter_mm,
               pooled_data$tongue_length - pooled_data$nectar_tube_depth_mm,
               0)
plot(temp) #A few outlyers, including negative values.

pooled_data[which(temp < 0),c(1,2,12,17)]
```
